Community-Conditioned Language Models

### 2020-11-02 paper/plot_macros.tex
add community infreence confusion plots

>>>>

\newcommand{\confusionplot}[1]{%
    \addplot[
        matrix plot*,
        shader=faceted,
        mesh/cols=46,
        point meta=explicit,
] table [x=actual_comm, y=confered_to, meta=avg_prob] {#1};
}

\newcommand{\confusiongroupplot}[2]{%
  \begin{groupplot}[
  group style={group size=2 by 1}, 
  enlargelimits=false,
  axis line style={draw=none},
  %axis equal,
  xmin=0, xmax=46,
  ymin=0, ymax=46,
  width=8cm,
  xticklabels={Advice,AskWomen,BabyBumps,CFB,Drugs,EDH,EarthPorn,Fantasy,GameDeals,GlobalOffensive,Jokes,Kappa,KerbalSpaceProgram,KotakuInAction,LifeProTips,MLS,MMA,MaddenUltimateTeam,TwoXChromosomes,Warframe,airsoft,bodybuilding,breakingmom,cars,cringe,eu4,exjw,explainlikeimfive,femalefashionadvice,food,heroesofthestorm,jailbreak,justneckbeardthings,oculus,pcmasterrace,photography,reddevils,relationships,rupaulsdragrace,stopdrinking,streetwear,techsupport,todayilearned,toronto,videos,xxfitness},
  yticklabels=none,
  xticklabel style={font=\tiny, rotate=90},
  xtick=data
    ]
    \nextgroupplot
    \confusionplot{#1}
    \nextgroupplot[colorbar right]
    \confusionplot{#2}
  \end{groupplot}
}
